IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-11-01 ms.tex
I added some more references to brown dwarf L/T work and added a crude spectrum for 2MASS J0835.

Brown dwarfs atmospheres are an intriguing environment to explore cloud composition, particle size and formation that also complement studies of exoplanet atmospheres.

The cloud layers may be studied from the direct spectroscopy and photometry of large populations of brown dwarf atmospheres.

In addition to the direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time.

@@

L dwarfs are found to be variable with periods of 1-100 hours \citep{bailer-jones1999bdvar,bailer-jones1999varevo}.
This variability is explained by a patchy clouds at the L/T transition \citep{marley2010patchyc}.

\citep{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) was a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
\caption{Sine fit amplitude versus wavelength for 2MASS J1821. The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}\label{fig:DHSRes}
\end{figure}

>>>>

Brown dwarfs atmospheres are an intriguing environment to explore cloud composition, particle size and formation that also complement studies of exoplanet atmospheres.
Their temperatures are cool enough that they span condensation points of many cloud-producing  compounds.

The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
In addition to these direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time.
In the case where the targets are bright enough, Doppler imaging can be used to map out the cloud structures on brown dwarfs as in \citet{crossfield2014dopplerimg}.

@@

L dwarfs are found to be variable with periods of 1-100 hours \citep{bailer-jones1999bdvar,bailer-jones1999varevo}.
This variability is explained by a patchy clouds at the L/T transition \citep{marley2010patchyc}.
Virtually all L dwarfs and most T dwarfs likely have photospheric heterogeneities that cause flux variations larger than 0.2\% in the near infrared \citep{metchev2015weatherII}

\citet{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) was a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.
\citet{burgaser2014irtf} observed the binary system Luhman 16 AB and used the more stable Luhman 16A as a simultaneous reference to measure spectral variability in Luhman 16B.

@@

\begin{figure*}[!]
\centering
\subfloat[2MASS J0835 - \colorbox{red}{fit needs more work} ]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{Sine fit amplitude versus wavelength for each brown dwarf. The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}
	\label{fig:ampSpect}
\end{figure*}

%    \begin{figure}[!ht]
%    \centering
%    \includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
%    \caption{Sine fit amplitude versus wavelength for 2MASS J1821. The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}\label{fig:DHSRes}
%    \end{figure}
